### 2015-01-10 paper/Content/sources.tex
Solution chapter

>>>>

\bibitem{AntLeiv14}
A. Leiva: \emph{MVP for Android: how to organize the presentation layer}, 2014,
[Online]. http://antonioleiva.com/mvp-android/ (retrieved 10-Jan-2015)

\bibitem{Fowler04}
M. Fowler: \emph{Inversion of Control Containers and the Dependency Injection pattern}, 2004,
[Online]. http://martinfowler.com/articles/injection.html (retrieved 10-Jan-2015)
